---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# constructive.example

This package serves as an example on how to extend {constructive}.

We build a new constructor for the class "tbl_df" (tibbles), using the deprecated
constructor `tibble::data_frame()`.

We also support a new class : "qr". This is the class of the object we get
after applying `base::qr()` to get the QR decomposition of a matrix.
We build a couple constructors for it.

The reconstruction is not perfect due to rounding errors so the function is not
a good fit for {constructive} but is a good use case for an example.



You might use it as a template, all useful constructive functions are imported
in "R/constructive.example-package.R"

## examples

Without {constructive.example}

```{r, error = TRUE}
library(constructive)

# will fail because the constructor is undefined
construct(dplyr::band_members, opts_tbl_df("data_frame"))

# will work but use the list constructor
A <- matrix(1:6, nrow = 3)
qr_A <- qr(A)
construct(qr_A)
```

With {constructive.example}

```{r, error = TRUE}
library(constructive.example)

# we can now choose our custom constructor for tbl_df objects
construct(dplyr::band_members, opts_tbl_df("data_frame"))

# and the "qr" class is now supported  
A <- matrix(1:6, nrow = 3)
qr_A <- qr(A)
construct(qr_A)

# the recreation was not perfect due to rounding errors but we're pretty close
construct_issues()
```

Other constructors

```{r}
# fall back on the next method, which is for lists
construct(qr_A, opts_qr("next"))

# use explicitly the list method (same result here)
construct(qr_A, opts_qr("list"))
```

corrupted objects

```{r}
corrupted <- structure(1:3, class = "qr")
# thanks to our implementation of is_corrupted_qr() we don't fail here but just fall
# back to the next method
construct(corrupted)
```

